Assignment 2

### 2019-06-29 ex2/report/report.tex
Add conclusion and misclassification

\section{Misclassification Examples}

@@

>>>>

\section{Misclassification Examples}
\autoref{tab:misclassified_instances} shows the total number of attack samples in the dataset of each attack class as well as what we call \textit{false positives} and \textit{false negatives}. The false negatives are simply the number of samples of each class that were falsely classified as benign even though they are actually attacks. 
The false positives are the classes of the attack samples that are the closest to a benign sample that was wrongly classified as being an attack.

\begin{table*}
\caption{Misclassified instances: \textit{false positives} shows the class of the attack sample that is closest to the misclassified benign sample; \textit{false negatives} shows how many attack samples of each class were falsely classified as benign.}
\label{tab:misclassified_instances}
\begin{tabular}{l l l l} 
\toprule 
Attack type & total number & false positives & false negatives \\
\midrule
Botnet:ARES  & 275 & 13 & 6 \\
Brute Force:FTP-Patator & 91 & 2 & 81 \\
Brute Force:SSH-Patator & 870 & 67 & 1 \\
DDoS:LOIT & 31887 & 0 & 29 \\
DoS / DDoS:DoS GoldenEye & 2490 & 2 & 1 \\
DoS / DDoS:DoS Hulk & 77998 & 4 & 1 \\
DoS / DDoS:DoS Slowhttptest & 1385 & 142 & 4 \\
DoS / DDoS:DoS slowloris & 1310 & 2 & 1 \\
DoS / DDoS:Heartbleed & 2 & 0 & 2 \\
Infiltration:Dropbox download & 25587 & 87 & 1783 \\
PortScan:PortScan - Firewall off & 53341 & 8 & 18 \\
PortScan:PortScan - Firewall on & 129 & 0 & 7 \\
Web Attack:Sql Injection & 6 & 0 & 1 \\
Web Attack:XSS & 233 & 69 & 100 \\
\bottomrule
\end{tabular}
\end{table*}

@@

We used a dataset for network anomaly detection and extracted features using an enhanced version of the CAIA feature vector. Then we trained two non-interpretable classifiers on the resulting data. The resulting random forest as well as the deep learning model performed very well on the dataset. As the next step we implemented a backdoor into the dataset. For this we had to find a feature that can actually be modified easily by an attacker. We found that the Time to Live (TTL) fulfills these criteria and implemented a backdoor in it by modifying the TTL of selected packets. The resulting backdoor was successfully detected by the classifier in nearly all cases. Furthermore, the accuracy of the classifier on the original dataset did not change significantly. However, the backdoor was clearly visible by inspecting the plots yielded by explainability methods. It follows that designers of network intrusion detection systems must carefully choose which feature vectors to use and to keep them small in order to reduce the attack surface for backdoors. Also, every intrusion detection system in production use should be thoroughly investigated with explainability methods to detect possible backdoors.
